Trustability of certification systems

### 2015-12-22 paper.tex
Old tech done, maybe need to rewrite the end of X509

\subsection{Thoughts about X.509 and PGP}
\label{thoughts_old}

@@

Because of a case of Google CA's usurpation, Google is working on a new system that can improve certification systems.

@@

>>>>

\subsection{Thoughts about X.509, CAs and PGP}
\label{thoughts_old}

To be used in a commercial way (for responsabilities purpose), X.509, CAs and PGP need a centralized certification control system. However, there is a struggle between this need of centralization and the internet architecture (that is decentralized). This show us the uselessness of centralized governement controls, since we have no central government on the internet which give a world governance.\\
So the question emerging in there is: how can we (and do we need to) have a main control on an internet environement, to assure the goodness of datas and legitimacy of interlocutors?\\
Some answers have been made since then (thus since the publication of the original article), answers that we are going to explain further.

@@

This protocol has been developped by a Google team few years ago \cite{LL11}. It is still in developpment \cite{certtransp2013} so it is not implemented and deployed yet. It also has to be improve, like everythign in computing sciences, in the early years.\\
CATA's purpose is a public list of all certificates that are emitted by CAs. Thus, clients are allowed to search in that public list, and verify that the received certificate is in that list, to be validate (if it is not in the list, it shall be rejected).\\
In that way, a(conscientious) domain administrator can have access to that list and monitor all fraudulent certificates for his domain.\\
For the moment, there are plenty of questions to answer like :
\begin{itemize}
	\item Who should hold those lists?
	\item How many lists should be created?
	\item How does the revokation should work?
	\item What should happen if a certificate is no longer available (path unreachable)?
\end{itemize}

@@

\bibitem{LL11} Ben Laurie and Adam Langley. Certificate authority transparency and auditability. http://www.links.
org/files/CertificateAuthorityTransparencyandAuditability.pdf, 2011.
